Dependent Object Types

### 2012-09-06 doc/candidacy/slides.tex
syntax

\begin{frame}[fragile]{${\nu}Obj$: Discussion}
\begin{itemize}
\item conflate the concepts of compound types (which inherit the
  members of several parent types) and mixin composition (which build
  classes from other classes and traits)
\item mixin composition is not commutative, unlike classical
  intersection types
\item in Scala, least upper bounds and greatest lower bounds do not always exist, e.g:
\end{itemize}
\begin{minted}{scala}
  trait A { type T <: A }
  trait B { type T <: B }
  // glb is approximated by an infinite sequence
  A with B { type T <: A with B { type T <: A with B {
    type T < ...
  }}}
\end{minted}
\end{frame}

>>>>

\begin{frame}[fragile]{${\nu}Obj$: Discussion}
\begin{itemize}
\item conflate the concepts of compound types (which inherit the
  members of several parent types) and mixin composition (which build
  classes from other classes and traits)
\item mixin composition is not commutative, unlike classical
  intersection types
\item in Scala, least upper bounds and greatest lower bounds do not always exist, e.g:
\end{itemize}
\begin{minted}{scala}
  trait A { type T <: A }
  trait B { type T <: B }
  // glb is approximated by an infinite sequence
  A with B { type T <: A with B { type T <: A with B {
    type T <: ...
  }}}
\end{minted}
\end{frame}
